\keywords{binaries: eclipsing --- methods: data analysis --- stars: fundamental parameters --- stars: AGB and post-AGB --- stars: oscillations (including pulsations)}

\section{Introduction}\label{intro}

% EDIT THE COMMENT BELOW TO SPECIFY WHICH FIGURES ARXIVER SHOULD USE
%@arxiver{fig1.pdf,fig4.png,fig15.eps}

% big picture context
Mass and radius are often-elusive stellar properties that are critical to understanding a star's past, present, and future. Eclipsing binaries are the only astrophysical laboratories that allow for a direct measurement of these and other fundamental physical parameters. Recently, however, observing solar-like oscillations in stars with convective envelopes has opened a window to stellar interiors and provided a new way to measure global stellar properties. A pair of asteroseismic scaling relations use the Sun as a benchmark and an empirical connection between these oscillations and a star's effective temperature to yield mass and radius \citep{kje95,hub10,mos13}.

While both the mass and radius scaling relations are useful, they remain relatively untested. [WAY TOO ELUSIVE: WE NEED TO CITE PREVIOUS WORKS AND REPHRASE. I WROTE THIS FOR A PROPOSAL, YOU CAN REPHRASE AND MELT IT WITH THE REST OF THE TEXT, (I PUT BIBTEX REFERENCES ON SLACK): "Given the importance of asteroseismology and its scaling laws, much recent effort has been carried out to test their validity. We may distinguish two kinds of approaches: those based on validating the relation between $\Delta\nu$ and stellar radius $R$ from models and simulated data \citep[e.g.][]{Stello_2009b,White_2011,Miglio_2013}, the others based on measuring $R$ on actual stars independently from asteroseismology \citep[e.g.][]{Huber_2011,Huber_2012,Silva_Aguirre_2012}.  All works indicated that radius estimates from asteroseismic scaling relations are precise up to a few percent. On the contrary, similar tests of mass determination for individual stars have not been possible so far. Indeed, most studies focused on the reliability of the $\Delta\nu$-$\bar\rho$ scaling and not on $\nu_{\rm{max}}$, because this observable has no secure theoretical basis, since it is not yet possible to make reliable predictions of the amplitude of stochastically excited modes and their dependence with frequency \citep{Christensen-Dalsgaard_2012}. " ]

 One notable exception is the red giant in the eclipsing binary KIC 8410637, which shows good agreement between Keplerian and asteroseismic mass and radius according to \citet{fra13}. However, a more recent analysis from \citet{hub14} indicates that the density of KIC 8410637 is underestimated by $\sim$7\,\% (1.8~$\sigma$, accounting for the density uncertainties), which results in an overestimate of the radius by $\sim$9\,\% (2.7~$\sigma$) and mass by $\sim$17\,\% (1.9~$\sigma$). In this work, we consider another important test case, KIC 9246715: an eclipsing binary with two nearly-identical red giant stars yet only one set of solar-like oscillations.

Evolved red giants are straightforward to characterize through pressure-mode solar-like oscillations in their convective zones, and red giant asteroseismology is quickly becoming an important tool to study stellar populations throughout the Milky Way \citep[for a review of this topic, see][]{cha13}. Compared to main-sequence stars, red giants oscillate with larger amplitudes and longer periods---several hours to days instead of minutes. Oscillations appear as spikes in the amplitude spectrum of a light curve that is sampled both frequently enough and for a sufficiently long duration. Given these two requirements, observations from the \emph{Kepler} space telescope taken every 29.4 minutes (long-cadence) over many 90-day quarters are ideal for asteroseismic studies of red giant stars.

\emph{Kepler}'s primary science goal is to find Earth-like exoplanets orbiting sun-like stars \citep{bor10}. However, in addition to successes in planet-hunting and suitability for red giant asteroseismology, \emph{Kepler} is also incredibly useful for studies of eclipsing binary stars. In fact, \emph{Kepler} has discovered numerous long-period eclipsing systems from consistent target monitoring over several years \citep{prs11,sla11}. Eclipsing binaries are important tools for understanding fundamental stellar properties, and in turn for testing stellar evolutionary models or determining distances. When radial velocity curves exist for both stars in an eclipsing binary, along with a well-sampled light curve, a full orbital solution can be found. Accurate masses and radii are straightforward to derive from such a solution; indeed, Kepler's third law applied in this way is the \emph{only} direct method for measuring stellar masses.

Taken together, red giants in eclipsing binaries (hereafter RG/EBs) that exhibit solar-like oscillations are ideal testbeds for asteroseismology. There are presently 15 known RG/EBs that show solar-like oscillations \citep{hek10,gau13,gau14} with orbital periods ranging from 15 to 1058 days, all found in the \emph{Kepler} field of view.

% Overview of paper
In this paper, we present physical parameters for the unique RG/EB KIC 9246715, which contains two nearly-identical red giants in a 171-day eccentric orbit. Only one set of solar-like oscillations is present. We find good agreement between photodynamic models and asteroseismology, but are unable to definitively say which star is oscillating. %We explore how star spots and tidal forces may influence the oscillations, verify that the two stars are consistent with a co-evolutionary history, and discuss how this system can inform future detailed studies of RG/EBs.

In \S \ref{data}, we describe how we acquire and process photometric and spectroscopic data, and \S \ref{rvs} explains our radial velocity extraction process. In \S \ref{atm}, we disentangle each star's contribution to the spectra to perform stellar atmosphere modeling. We then present our final orbital solution and physical parameters for KIC 9246715 in \S \ref{model}. Finally, \S \ref{discuss} compares our results with those from asteroseismology and discusses the connection between solar-like oscillations, stellar evolution, effects such as star spots and tidal forces, and implications for future RG/EB studies.

  
  
  
  
  
  
  