\subsection{Stellar evolution and tidal forces}\label{tides}

Over the course of KIC 9246715's life, both stars have evolved in tandem to reach the configuration we see today. We quantify this with simple stellar evolution models created using the Modules for Experiments in Stellar Astrophysics (MESA) code \citep{pax11,pax13,pax15}. Figure \ref{fig:mesa} presents a suite of models with various initial stellar masses. Recall that the masses and radii of each star are $M_1 = 2.16 \pm 0.04\ M_{\odot}$, $M_2 = 2.14 \pm 0.03\ M_{\odot}$, $R_1 = 7.90 \pm 0.04 \ R_{\odot}$, $R_2 = 8.33 \pm 0.04 \ R_{\odot}$. The stage of each star's life as it ages in Figure \ref{fig:mesa} is color-coded, and two lines of constant radii (corresponding to Star 1 and Star 2) are shown. From this, we conclude that both stars are indeed coeval, are both presently on the red giant branch, and are too small by $\sim 1 \ R_\odot$ to have evolved past this stage onto the red clump.

We explore several possibilities to explain why these stars appear to be on the red giant branch when the asteroseismic period spacing suggested they were on the red clump (I WILL ELABORATE ON EACH OF THESE AND DRAW SOME KIND OF CONCLUSION):
\begin{itemize}
\item mass loss?
\item overshooting?
\item low amplitude modes physically change convection, and thus evolution?
\item period spacing is weird and rotational splitting of mixed modes is annoying?
\end{itemize}

Beyond a pair of simple stellar evolution models, it is important to consider how each star has affected the other over time. To estimate how we expect tidal forces to change the orbital eccentricity, we follow the approach of \citet{ver95}, who use a theory of the equilibrium tide first proposed by \citet{zah77} to calculate a timescale for orbit circularization, $\tau_c$, as a star evolves. The total change in eccentricity over a detached binary's lifetime, $\Delta \ln e$, is found by integrating $1/\tau_c \equiv \rm{d} \ln e / \rm{d}t$:

\begin{equation}\label{circ}
\Delta \ln e = \int_0^t \frac{\rm{d}t'}{\tau_c(t')}.
\end{equation}

To approximate the case of KIC 9246715, we assume the stars are sufficiently separated to make $a$ constant over time, and we further assume no mass loss. We can then use equations 5 and 6 from \citet{ver95} to calculate the expected change in orbital eccentricity:

\begin{equation}\label{tide1}
\Delta \ln e = -1.7 \times 10^{-5} \ f \ {\left( \frac{M}{M_{\odot}} \right)}^{-11/3} \ q(1+q)^{-5/3} \ I(t) {\left( \frac{P_{\rm{orb}}}{\rm{day}} \right)}^{-16/3},
\end{equation}

where $f$ is a factor of order unity, $q$ is the ratio of the companion star's mass $M_2$ to the primary star's mass $M$, and

\begin{equation}
I(t) \equiv \int_0^t \left( \frac{T_{\rm{eff}}(t')}{4500 \rm{K}} \right)^{4/3} \ \left( \frac{M_{\rm{env}}(t')}{M_{\odot}} \right)^{2/3} \ \left( \frac{R(t')}{R_{\odot}} \right)^8 \ dt',
\end{equation}

where $M_{\rm{env}}$ is the mass of the convective envelope of the primary star. It is important to note that \citet{ver95} assumed circularization would proceed by a small secondary star (main sequence or white dwarf) imposing an equilibrium tide on a large giant, while the situation with KIC 9246715 is more complicated. For a thorough review of tidal forces in stars, see \citet{ogi14}.

For the MESA model described above, we compute $\Delta \ln e = 1.84$ up until $t = 9 \times 10^8$ years, indicating that the eccentricity should have changed by more than 1 over the star's lifetime. The two coeval stars in KIC 9246715 have very similar masses, radii, and temperatures, so this rough calculation is valid both for Star 1 acting on Star 2 and vice versa. In either case, this means that regardless of KIC 9246715's original eccentricity, it should have evolved to zero by the present day, when both stars are in the red clump phase. The observed $e = 0.35$ is inconsistent. DISCUSS THE RESULT FURTHER.

Tidal forces also tend to synchronize a binary star's orbit with the stellar rotation period, generally on shorter timescales than required for circularization \citep{ogi14}. Hints of KIC 9246715's stellar rotation behavior are present throughout this study: quasi-periodic light curve variability on the order of half the orbital period (Section \ref{discuss}), a star spot present during one primary eclipse event only (Section \ref{segment}), a constraint on $v \sin i$ from spectra (Section \ref{parameters}), and asteroseismic period spacing consistent with red clump stars yet not clear enough to measure a robust core rotation rate (Section \ref{discuss}). 

WRITE MORE ABOUT SYNCHRONIZATION OR LACK THEREOF HERE, AND CLEAN THE FOLLOWING PARAGRAPHS UP.

\textit{Centrifugal forces dissipate energy that would cause circularization. Causes individual rotations to synchronize (usually synchronization happens first, and circularization happens second). Neither of those things have happened here, but it seems like the rotation knows about the orbit (based on quasiperiodic spot modulations, not necessarily vsini, and certainly not a robust core rotation measure), so SOMETHING has happened... just not synchronization. This ``should have'' happened even faster since it's two RGs, not a RG + MS (or WD). The fact that both of them have convection zones that could be causing this centrifugal force situation means that this should have happened a long time ago in a hand-wavey sort of way.

The fact that only one star is oscillating points to how tidal activity may affect oscillations.
Important for other people because over half of cool stars should be in binaries! Using RGs to probe the galaxy has to be done carefully because of external influences of binarity on oscillations.}
  

  
  
  
  
  
  
  